\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\input{../Comments.text}
\input{../Common.text}

\begin{document}

\title{System Verification and Validation Plan for \progname{}} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Feb 10, 2026 & 1.0 & Initial draft\\
Feb 13, 2026 & 1.1 & Adjust according to feedback\\
March 29, 2026 & 1.2 & Adjust according to feedback\\
Apr 21, 2026 & 1.3 & Adjust according to smith's feedback\\
\bottomrule
\end{tabularx}

~\\
% \wss{The intention of the VnV plan is to increase confidence in the software.
% However, this does not mean listing every verification and validation technique
% that has ever been devised.  The VnV plan should also be a \textbf{feasible}
% plan. Execution of the plan should be possible with the time and team available.
% If the full plan cannot be completed during the time available, it can either be
% modified to ``fake it'', or a better solution is to add a section describing
% what work has been completed and what work is still planned for the future.}

% \wss{The VnV plan is typically started after the requirements stage, but before
% the design stage.  This means that the sections related to unit testing cannot
% initially be completed.  The sections will be filled in after the design stage
% is complete.  the final version of the VnV plan should have all sections filled
% in.}

\newpage

\tableofcontents

% \listoftables
% \wss{Remove this section if it isn't needed}

% \listoffigures
% \wss{Remove this section if it isn't needed}

\newpage

\section{Symbols, Abbreviations, and Acronyms}

Identical to the same section in SRS document \citep{SRS}.

% \renewcommand{\arraystretch}{1.2}
% \begin{tabular}{l l} 
%   \toprule		
%   \textbf{symbol} & \textbf{description}\\
%   \midrule 
%   T & Test\\
%   \bottomrule
% \end{tabular}\\

% \wss{symbols, abbreviations, or acronyms --- you can simply reference the SRS
%   \citep{SRS} tables, if appropriate}

% \wss{Remove this section if it isn't needed}

\newpage

\pagenumbering{arabic}

This document presents the Verification and Validation (V\&V) plan for \progname{}. 
It explains how the software and related artifacts will be reviewed, tested, and evaluated to provide confidence that the implemented pipeline satisfies its documented requirements and is suitable for its intended use.

\section{General Information}


\subsection{Summary}

% \wss{Say what software is being tested.  Give its name and a brief overview of
%   its general functions.}

This project is for comparing candidate speech representations by how well they predict neural responses during speech recognition. 
Given speech stimuli and corresponding MEG recordings, the system constructs time-aligned predictors from multiple
sources, fits ridge-regularized multivariate Temporal Response Function (mTRF) encoding models over a specified lag window, and produces quantitative scores and summaries to support reproducible scientific interpretation.



\subsection{Objectives}

% \wss{State what is intended to be accomplished.  The objective will be around
%   the qualities that are most important for your project.  You might have
%   something like: ``build confidence in the software correctness,''
%   ``demonstrate adequate usability.'' etc.  You won't list all of the qualities,
%   just those that are most important.}

% \wss{You should also list the objectives that are out of scope.  You don't have 
% the resources to do everything, so what will you be leaving out.  For instance, 
% if you are not going to verify the quality of usability, state this.  It is also 
% worthwhile to justify why the objectives are left out.}

% \wss{The objectives are important because they highlight that you are aware of 
% limitations in your resources for verification and validation.  You can't do everything, 
% so what are you going to prioritize?  As an example, if your system depends on an 
% external library, you can explicitly state that you will assume that external library 
% has already been verified by its implementation team.}
The primary objectives of this Verification and Validation (V\&V) plan are to:

\begin{itemize}
  \item Build confidence that correctly performs the end-to-end
  workflow specified in the SRS. 
  \item Demonstrate that comparisons across predictors are fair and reproducible under a consistent protocol.
  \item Provide evidence that the produced outputs are traceable and inspectable, enabling experiments to be repeated and extended with minimal ambiguity.
\end{itemize}

The following objectives are explicitly out of scope for this project:

\begin{itemize}
  \item \textbf{Biological validity claims:} \progname{} will not validate neuroscientific claims beyond what is implied by predictive performance. In particular, this project will not claim that higher prediction performance implies a true mechanistic explanation of the brain.
  \item \textbf{Formal verification:} This project will not provide formal proofs of correctness. 
  The project resources are insufficient for a formal-methods effort.
  \item \textbf{Independent verification of external libraries:} This project assume that widely used scientific libraries ( NumPy/SciPy, PyTorch, MNE-Python, Eelbrain) have been verified by their development
  communities.
  \item \textbf{Clinical-grade security:} The system is research
  software. Security hardening and clinical deployment requirements are out of scope.
\end{itemize}







\subsection{Extras}

% \wss{Summarize the extras (if any) that were tackled by this project.  Extras
% can include usability testing, code walkthroughs, user documentation, formal
% proof, GenderMag personas, Design Thinking, etc.  Extras should have already
% been approved by the course instructor as included in your problem statement.
% You can use a pull request to update your extras (in TeamComposition.csv or
% Repos.csv) if your plan changes as a result of the VnV planning exercise.}

\begin{itemize}
  \item \textbf{Code walkthrough:} A structured walkthrough session will be conducted using the implementation. The walkthrough will examine whether each functional requirement is mapped to the intended modules, instance models, and verification activities. It will also inspect the consistency between the implementation, planned tests, and documented assumptions.
  
  \item \textbf{User manual:} A short user manual will be provided with environment setup instructions, required dependencies, configuration examples, and example commands for running one end-to-end experiment, including model training, predictor extraction, TRF fitting, and score computation.
\end{itemize}




\subsection{Relevant Documentation}

% \wss{Reference relevant documentation.  This will definitely include your SRS
%   and your other project documents (design documents, like MG, MIS, etc).  You
%   can include these even before they are written, since by the time the project
%   is done, they will be written.  You can create BibTeX entries for your
%   documents and within those entries include a hyperlink to the documents.}

% \citet{SRS}

% \wss{Don't just list the other documents.  You should explain why they are relevant and 
% how they relate to your VnV efforts.}

\begin{itemize}
  \item Software Requirements Specification (SRS)  Available at: \href{https://github.com/Krozix-2026/cas741-speech-trf/blob/main/docs/SRS/SRS.tex}{SRS}.
  \item Module Guide (MG). Available at: \href{https://github.com/Krozix-2026/cas741-speech-trf/blob/main/docs/Design/SoftArchitecture/MG.tex}{MG}.
  \item Module Interface Specification (MIS). Available at: \href{https://github.com/Krozix-2026/cas741-speech-trf/blob/main/docs/Design/SoftDetailedDes/MIS.tex}{MIS}.
\end{itemize}




\section{Plan}

% \wss{Introduce this section.  You can provide a roadmap of the sections to
%   come.}
This section describes the people and processes used to verify and validate \progname{}. 
It covers document reviews, implementation verification, automated tools, and the approach to validating that the software meets stakeholder needs for reproducible scientific comparison.



\subsection{Verification and Validation Team}

\begin{table}[]
\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule 
    \textbf{Member} & \textbf{Role} & \textbf{Responsibilities} \\
\midrule
    Xiao Shao & Developer & Produce the VnV Plan and refine based on feedback \\
    Dr. Spencer Smith & Course Instructor & Provides feedback on engineering principles \\
    Dr. Christian Brodbeck & Domain Expert & Provides domain-specific information on requirements and validation \\
    Yanyu Wu & Reviewer & Provides feedback on VnV plan \\
\bottomrule
\end{tabularx}
\caption{Verification and Validation Team}
\end{table}



\subsection{SRS Verification}

% \wss{List any approaches you intend to use for SRS verification.  This may
%   include ad hoc feedback from reviewers, like your classmates (like your
%   primary reviewer), or you may plan for something more rigorous/systematic.}

% \wss{If you have a supervisor for the project, you shouldn't just say they will
% read over the SRS.  You should explain your structured approach to the review.
% Will you have a meeting?  What will you present?  What questions will you ask?
% Will you give them instructions for a task-based inspection?  Will you use your
% issue tracker?}

% \wss{Maybe create an SRS checklist?}

SRS verification will be conducted through a structured review process:

\begin{itemize}
    \item \textbf{Checklist-based inspection:} The author will inspect the SRS using the course SRS checklist and a project-specific checklist focused on traceability between assumptions, theoretical models, instance models, data definitions, and requirements.  
    Checklist link: \href{https://github.com/Krozix-2026/cas741-speech-trf/tree/main/docs/Checklists}{Course SRS Checklist}.

    \item \textbf{Peer review:} A classmate reviewer will review the SRS using the same checklist and written review instructions on Github. The review will focus on missing assumptions, ambiguous terminology, inconsistent references, and mismatches between requirements and instance models. Review comments will be recorded in the Github as issues or written review notes.   
    Review record: \href{https://github.com/Krozix-2026/cas741-speech-trf/issues}{SRS Review Comments}.

    \item \textbf{Supervisor review:} The SRS will be discussed in a scheduled walkthrough meeting with the supervisor or instructor. The meeting will be structured around the problem scope, assumptions, requirements, theoretical and instance models, and traceability matrices. Action items from the meeting will be recorded and used to revise the document and framework.  
    Meeting notes or summary: \href{https://docs.google.com/document/d/1MB4mZMU3GUZd5zrZ7lYlEK12WPLXRYUR8ijGftzUFMo/edit?tab=t.0}{Supervisor Review Notes}.
\end{itemize}







\subsection{Design Verification}

% \wss{Plans for design verification}

% \wss{The review will include reviews by your classmates}

% \wss{Create a checklists?}

A classmate reviewer will review the MG and MIS using the corresponding course checklists and reviewer instructions. The review will focus on whether the module decomposition, module interfaces, and information hiding decisions are consistent with the SRS and with the planned implementation. Review comments will be recorded in the Github.  
MG review record: \href{https://github.com/Krozix-2026/cas741-speech-trf/issues}{MG Review Comments}.  
MIS review record: \href{https://github.com/Krozix-2026/cas741-speech-trf/issues}{MIS Review Comments}.




\subsection{Verification and Validation Plan Verification}

% \wss{The verification and validation plan is an artifact that should also be
% verified.  Techniques for this include review and mutation testing.}

% \wss{The review will include reviews by your classmates}

% \wss{Create a checklists?}
A classmate reviewer will review the VnV plan using the course checklist and the reviewer instructions provided by the author. The review will focus on whether each requirement and correctness property is mapped to a concrete verification or validation activity, and whether the proposed tests are specific and reproducible. Review comments will be recorded in the Github.  
VnV review record: \href{https://github.com/Krozix-2026/cas741-speech-trf/issues}{VnV Review Comments}.




\subsection{Implementation Verification}


\begin{itemize}
  \item \textbf{Unit testing:} Automated tests are used for core modules
  (alignment, lagged design matrix construction, ridge fitting, scoring, and
  artifact logging). These tests cover both normal behavior and edge cases,
  including shape mismatches, invalid inputs, and missing or NaN values.

  \item \textbf{Integration testing:} End-to-end pipeline tests on Librispeech dataset are used to verify correct interaction among modules,
  including data loading, predictor construction, temporal alignment, model
  fitting, scoring, and result generation.

  \item \textbf{Requirement-based verification:} System-level checks are used to
  confirm that the implementation satisfies the intended functional behavior
  described in the SRS. For example, tests verify that all predictors specified
  in an experiment are evaluated under the same protocol, that cross-validated
  scores are aggregated as specified, that baseline-referenced gains are
  computed and recorded, and that invalid inputs are rejected before model
  fitting.

  \item \textbf{Reproducibility and regression checks:} Repeated runs under the
  same configuration are compared to confirm stable behavior, and regression
  tests are used to detect unintended changes in outputs after implementation
  updates.
\end{itemize}




\subsection{Automated Testing and Verification Tools}

% \wss{What tools are you using for automated testing.  Likely a unit testing
%   framework and maybe a profiling tool, like ValGrind.  Other possible tools
%   include a static analyzer, make, continuous integration tools, test coverage
%   tools, etc.  Explain your plans for summarizing code coverage metrics.
%   Linters are another important class of tools.  For the programming language
%   you select, you should look at the available linters.  There may also be tools
%   that verify that coding standards have been respected, like flake9 for
%   Python.}

% \wss{If you have already done this in the development plan, you can point to
% that document.}

% \wss{The details of this section will likely evolve as you get closer to the
%   implementation.}

\begin{itemize}
  \item \textbf{pytest} for unit and integration tests, with markers for slow tests.
  \item \textbf{GitHub Actions} to automates CI/CD workflows to run tests, checks, and deployments on every push or pull request.
  \item \textbf{flake8} for linting and black for formatting to
  enforce coding standards.
  \item \textbf{Continuous Integration} on the repository to run tests and checks on each merge request, ensuring regressions are caught early.
\end{itemize}





\subsection{Software Validation}

% \wss{If there is any external data that can be used for validation, you should
%   point to it here.  If there are no plans for validation, you should state that
%   here.}

% \wss{You might want to use review sessions with the stakeholder to check that
% the requirements document captures the right requirements.  Maybe task based
% inspection?}

% \wss{For those capstone teams with an external supervisor, the Rev 0 demo should 
% be used as an opportunity to validate the requirements.  You should plan on 
% demonstrating your project to your supervisor shortly after the scheduled Rev 0 demo.  
% The feedback from your supervisor will be very useful for improving your project.}

% \wss{For teams without an external supervisor, user testing can serve the same purpose 
% as a Rev 0 demo for the supervisor.}

% \wss{This section might reference back to the SRS verification section.}

Out of scope for this project.



\section{System Tests}

% \wss{There should be text between all headings, even if it is just a roadmap of
% the contents of the subsections.}

This section lists system-level tests that collectively cover the functional and nonfunctional requirements in the SRS. 
Tests are grouped by major workflow areas: input/validation, predictor construction and alignment, TRF fitting, evaluation
and gain computation.

\paragraph{Definition of Clean Environment}
A clean environment means that the test begins from a fresh execution state with no residual files, caches, in-memory objects, or configuration side effects from previous runs, except for the inputs and configuration explicitly specified in the current test case.

\subsection{Tests for Functional Requirements}

% \wss{Subsets of the tests may be in related, so this section is divided into
%   different areas.  If there are no identifiable subsets for the tests, this
%   level of document structure can be removed.}

% \wss{Include a blurb here to explain why the subsections below
%   cover the requirements.  References to the SRS would be good here.}
The functional tests below cover the end-to-end workflow implied by the SRS requirements. 



% \subsubsection{Area of Testing1}

% \wss{It would be nice to have a blurb here to explain why the subsections below
%   cover the requirements.  References to the SRS would be good here.  If a section
%   covers tests for input constraints, you should reference the data constraints
%   table in the SRS.}
		
% \paragraph{Title for Test}

% \begin{enumerate}

% \item{test-id1\\}

% Control: Manual versus Automatic
					
% Initial State: 
					
% Input: 
					
% Output: \wss{The expected result for the given inputs.  Output is not how you
% are going to return the results of the test.  The output is the expected
% result.}

% Test Case Derivation: \wss{Justify the expected value given in the Output field}
					
% How test will be performed: 
					
% \item{test-id2\\}

% Control: Manual versus Automatic
					
% Initial State: 
					
% Input: 
					
% Output: \wss{The expected result for the given inputs}

% Test Case Derivation: \wss{Justify the expected value given in the Output field}

% How test will be performed: 

% \end{enumerate}

% \subsubsection{Area of Testing2}

\subsubsection{Input and Configuration Validation}

\paragraph{Input schema and basic validity checks}


\begin{enumerate}

\item{FR-01 (Invalid MEG sampling frequency)\\}
Control: Automatic \\
Initial State: Clean environment; a valid MEG metadata record extracted from an
Appleseed MEG file is available (for example, via a test fixture or a copied
header from one valid file). \\
Input: Start from a valid Appleseed MEG metadata record and set the sampling
frequency field \texttt{fs} to an invalid value with \texttt{fs = 0}
(or any \texttt{fs < 0}). \\
Output: The system rejects the run and reports an
\texttt{InvalidConfigurationError} (or equivalent validation failure) that
identifies the MEG sampling frequency field and states that the value must be
strictly positive. \\
Test Case Derivation: R1 \\
How test will be performed: In pytest, load a valid Appleseed-derived metadata
fixture, modify the field \texttt{fs} to \texttt{0}, call the input or metadata
validation function, and assert that validation fails with an error message
containing both the field name \texttt{fs} and the constraint that the sampling
frequency must be positive.


\item{FR-02 (Unsupported deep model type)\\}
Control: Automatic \\
Initial State: Clean environment; a valid model configuration is loaded. \\
Input: Start from a valid model configuration and set the field
\texttt{model.type} to a specific unsupported identifier, such as
\texttt{"unsupported\_model"}. \\
Output: The system rejects the configuration and reports that the specified
model type is unsupported. The error message shall also list the supported model
types (for example, \texttt{RNN}, \texttt{LSTM}, \texttt{GRU},
\texttt{Transformer}). \\
Test Case Derivation: R2 \\
How test will be performed: In pytest, load a valid model configuration, change
\texttt{model.type} to \texttt{"unsupported\_model"}, call the model
configuration validation function, and assert that validation fails with an
error message that includes the invalid identifier and the supported model type
list.

\item{FR-03 (Invalid model architecture hyperparameters)\\}
Control: Automatic \\
Initial State: Clean environment; a valid model configuration is loaded. \\
Input: Create invalid configuration variants from the valid model configuration
by setting one hyperparameter at a time to an invalid value:
\texttt{num\_layers = 0}, \texttt{hidden\_size = 0}, and
\texttt{dropout = 1.2}. \\
Output: For each invalid configuration, the system rejects the configuration
and reports a validation error that identifies the invalid hyperparameter name
and states the violated constraint (for example,
\texttt{num\_layers > 0}, \texttt{hidden\_size > 0}, or
\texttt{dropout \(\in [0,1)\)}). \\
Test Case Derivation: R2 \\
How test will be performed: In pytest, parameterize the three invalid
configuration variants, call the model configuration validation function for
each case, and assert that validation fails with an error message mentioning the
corresponding hyperparameter name and constraint.

\item{FR-04 (Model input feature dimension mismatch)\\}
Control: Automatic \\
Initial State: Clean environment; a valid model configuration is loaded, and the configured model expects input tensors with feature dimension $D_{\mathrm{exp}}$ (for example, the number of acoustic features or gammatone channels specified in the configuration). \\
Input: Construct a small synthetic input batch whose last dimension is
$D_{\mathrm{obs}} \neq D_{\mathrm{exp}}$; for example, if the model expects
$D_{\mathrm{exp}} = 64$, provide an input tensor with feature dimension
$D_{\mathrm{obs}} = 80$. \\
Output: The system rejects training or representation extraction and reports a dimension-mismatch error identifying both the expected feature dimension and the observed feature dimension. \\
Test Case Derivation: R2 \\
How test will be performed: In pytest, load a valid model configuration,
construct a synthetic batch with mismatched feature dimension, call the model input validation or forward-pass entry point, and assert that an exception is raised before any optimizer step, with an error message containing both $D_{\mathrm{exp}}$ and $D_{\mathrm{obs}}$.


\item{FR-05 (LibriSpeech manifest integrity)\\}
Control: Automatic \\
Initial State: Clean environment; a valid LibriSpeech-style manifest or metadata table is available, and the dataset root path is configured (for example, \texttt{train-clean-100}). \\
Input: Create a test manifest derived from the valid manifest in which one row references a missing audio file or a missing transcript file. The modified row identifier shall be recorded in the test input. \\
Output: The system rejects dataset loading and reports the missing file path together with the identifier of the manifest row that contains the invalid reference. \\
Test Case Derivation: R2 \\
How test will be performed: In pytest, load the modified manifest, call the
dataset-loading or manifest-validation function, and assert that loading fails with an error message containing the missing path and the corresponding row identifier.



\item{FR-06 (Incompatible predictor time axis for alignment)\\}
Control: Automatic \\
Initial State: Clean environment; MEG data are loaded with a known MEG sampling rate and time grid. \\
Input: Provide a predictor time series whose time axis is incompatible with the MEG time grid; for example, omit the predictor timestamps entirely, provide a non-monotonic predictor time axis, or provide timestamps whose covered time range does not overlap the MEG segment to be aligned. \\
Output: The system rejects alignment and reports a validation error identifying the predictor time axis and the MEG time grid as incompatible for alignment. \\
Test Case Derivation: R4 \\
How test will be performed: In pytest, create a small synthetic MEG time grid and a predictor with an incompatible time axis, call the predictor-alignment function, and assert that alignment fails with an error message describing the specific incompatibility.



\item{FR-07 (Inconsistent evaluation protocol across predictors)\\}
Control: Automatic \\
Initial State: Clean environment; at least two predictor definitions are
configured (for example, a gammatone baseline and one hidden-state predictor). \\
Input: Configure the two predictors with different evaluation protocol settings;
for example, assign different lag windows, different lag discretizations,
different cross-validation partitions, or different regularization grids. \\
Output: The system rejects the evaluation run and reports which protocol fields differ across predictors. \\
Test Case Derivation: R7 \\
How test will be performed: In pytest, define two predictors, intentionally set one protocol field to a conflicting value for one predictor, call the evaluation protocol validation function, and assert that validation fails with an error message listing the conflicting protocol field names.



\item{FR-08 (Encoding score computation returns invalid or missing results)\\}
Control: Automatic \\
Initial State: Clean environment; one predictor matrix and one MEG response
matrix are available on the same time grid. \\
Input: Construct a test case in which the score is undefined or invalid; for example, (a) insert a \texttt{NaN} value into the predictor matrix, or (b) provide a constant response signal that makes Pearson correlation undefined. \\
Output: The system rejects scoring and reports a scoring error identifying the cause of invalidity, such as the presence of \texttt{NaN} values in the predictor matrix or undefined correlation due to a constant response signal. \\
Test Case Derivation: R7 \\
How test will be performed: In pytest, construct small synthetic matrices for the predictor and response, evaluate the scoring function under each invalid case, and assert that scoring fails with an error message indicating the specific cause of invalidity.





\end{enumerate}









\subsection{Tests for Nonfunctional Requirements}

% \wss{The nonfunctional requirements for accuracy will likely just reference the
%   appropriate functional tests from above.  The test cases should mention
%   reporting the relative error for these tests.  Not all projects will
%   necessarily have nonfunctional requirements related to accuracy.}

% \wss{For some nonfunctional tests, you won't be setting a target threshold for
% passing the test, but rather describing the experiment you will do to measure
% the quality for different inputs.  For instance, you could measure speed versus
% the problem size.  The output of the test isn't pass/fail, but rather a summary
% table or graph.}

% \wss{Tests related to usability could include conducting a usability test and
%   survey.  The survey will be in the Appendix.}

% \wss{Static tests, review, inspections, and walkthroughs, will not follow the
% format for the tests given below.}

% \wss{If you introduce static tests in your plan, you need to provide details.
% How will they be done?  In cases like code (or document) walkthroughs, who will
% be involved? Be specific.}

% \subsubsection{Area of Testing1}
		
% \paragraph{Title for Test}

% \begin{enumerate}

% \item{test-id1\\}

% Type: Functional, Dynamic, Manual, Static etc.
					
% Initial State: 
					
% Input/Condition: 
					
% Output/Result: 
					
% How test will be performed: 
					
% \item{test-id2\\}

% Type: Functional, Dynamic, Manual, Static etc.
					
% Initial State: 
					
% Input: 
					
% Output: 
					
% How test will be performed: 

% \end{enumerate}

% \subsubsection{Area of Testing2}

\subsubsection{Usability}

\paragraph{Usability survey acceptance test}

\begin{enumerate}

\item{NFR-01\\}
Type: Manual \\
Initial State: An alpha version of \progname{} is available; a user group consisting of graduate students or researchers familiar with speech/MEG analysis is selected. \\
Input/Condition: Participants complete a short end-to-end task (configure paths, run one training-or-load step, extract representations as predictors, fit mTRF, and open the final comparison summary) and then complete a usability survey questionnaire. \\
Output/Result: At least 80\% of respondents rate the software as easy to use. \\
How test will be performed: Collect questionnaire results; compute the percentage of ``easy to use'' responses and verify it is larger than 80\%.

\end{enumerate}

\subsubsection{Maintainability}

\paragraph{Likely-change effort threshold test}

\begin{enumerate}

\item{NFR-02\\}
Type: Automatic, Manual \\
Initial State: Baseline development time is recorded for the original implementation; the codebase is under version control and includes a basic test suite. \\
Input/Condition: Select one likely change (e.g., adding one new deep model type, or adding one new predictor extraction option such as an additional layer output) and implement it by a developer with relevant domain knowledge. \\
Output/Result: The measured effort to implement the chosen likely change is less than 10 lines of the code, and existing tests still pass. \\
How test will be performed: Track engineering time using commits/issues; compare total effort against the recorded baseline and confirm it satisfies the threshold.

\end{enumerate}

\subsubsection{Portability}

\paragraph{Cross-platform installation and execution test}

\begin{enumerate}

\item{NFR-03\\}
Type: Manual \\
Initial State: Clean Windows, macOS, and Linux environments prepared. \\
Input/Condition: Install \progname{} and run a small smoke-test workflow on each OS using a bundled demo configuration and a small subset of Librispeech. \\
Output/Result: The pipeline installs and runs successfully on Windows, macOS, and Linux and produces the expected output files for the workflow. \\
How test will be performed: Create different workflows for each OS on GitHub Actions (or run the same documented steps manually if CI is unavailable) and record pass/fail logs.

\end{enumerate}

\subsubsection{Reproducibility}

\paragraph{Repeat-run consistency test}

\begin{enumerate}

\item{NFR-04\\}
Type: Automatic \\
Initial State: A fixed configuration file is available; the run uses a fixed random seed; the same input data are used. \\
Input/Condition: Run the same end-to-end workflow twice (training-or-load, predictor extraction, mTRF fitting, report generation) without changing any configuration. \\
Output/Result: The two runs produce consistent results for the reported summary metrics and the same set of output artifacts (same filenames and structure). \\
How test will be performed: Run the pipeline twice and compare the generated summary files for consistency.

\end{enumerate}

\subsubsection{Performance}

\paragraph{End-to-end runtime baseline benchmark}

\begin{enumerate}

\item{NFR-05\\}
Type: Automatic \\
Initial State: A small benchmark configuration is prepared (short audio duration, small MEG segment, minimal cross-validation). \\
Input/Condition: Run the full workflow on the benchmark configuration. \\
Output/Result: The workflow completes successfully within a reasonable amount of time on a standard workstation without running out of memory. \\
How test will be performed: Record wall-clock time and check that the run completes and produces the expected outputs; store the timing log with the run artifacts.

\end{enumerate}



















\subsection{Traceability Between Test Cases and Requirements}

% \wss{Provide a table that shows which test cases are supporting which
%   requirements.}

\begin{table}[h]
\centering
\begin{tabularx}{0.85\textwidth}{p{2.2cm}X}
\toprule
\textbf{Requir.} & \textbf{Test Cases} \\
\midrule
R1  & FR-01 \\
R2  & FR-02 - FR-05 \\
R3  & FR-06 \\
R4  & FR-07 \\
R5  & FR-08 \\
\midrule
NFR1 & NFR-01 \\
NFR2 & NFR-02 \\
NFR3 & NFR-03 \\
NFR4 & NFR-03 \\
\bottomrule
\end{tabularx}
\caption{Traceability Between Requirements and Test Cases}
\label{Table:Req_Test_Trace}
\end{table}



\section{Unit Test Description}

% \wss{This section should not be filled in until after the MIS (detailed design
%   document) has been completed.}

% \wss{Reference your MIS (detailed design document) and explain your overall
% philosophy for test case selection.}  

% \wss{To save space and time, it may be an option to provide less detail in this section.  
% For the unit tests you can potentially layout your testing strategy here.  That is, you 
% can explain how tests will be selected for each module.  For instance, your test building 
% approach could be test cases for each access program, including one test for normal behaviour 
% and as many tests as needed for edge cases.  Rather than create the details of the input 
% and output here, you could point to the unit testing code.  For this to work, you code 
% needs to be well-documented, with meaningful names for all of the tests.}

\subsection{Unit Testing Scope}

% \wss{What modules are outside of the scope.  If there are modules that are
%   developed by someone else, then you would say here if you aren't planning on
%   verifying them.  There may also be modules that are part of your software, but
%   have a lower priority for verification than others.  If this is the case,
%   explain your rationale for the ranking of module importance.}

% \subsection{Tests for Functional Requirements}

% \wss{Most of the verification will be through automated unit testing.  If
%   appropriate specific modules can be verified by a non-testing based
%   technique.  That can also be documented in this section.}

% \subsubsection{Module 1}

% \wss{Include a blurb here to explain why the subsections below cover the module.
%   References to the MIS would be good.  You will want tests from a black box
%   perspective and from a white box perspective.  Explain to the reader how the
%   tests were selected.}

% \begin{enumerate}

% \item{test-id1\\}

% Type: \wss{Functional, Dynamic, Manual, Automatic, Static etc. Most will
%   be automatic}
					
% Initial State: 
					
% Input: 
					
% Output: \wss{The expected result for the given inputs}

% Test Case Derivation: \wss{Justify the expected value given in the Output field}

% How test will be performed: 
					
% \item{test-id2\\}

% Type: \wss{Functional, Dynamic, Manual, Automatic, Static etc. Most will
%   be automatic}
					
% Initial State: 
					
% Input: 
					
% Output: \wss{The expected result for the given inputs}

% Test Case Derivation: \wss{Justify the expected value given in the Output field}

% How test will be performed: 

% \item{...\\}
    
% \end{enumerate}

% \subsubsection{Module 2}



\subsection{Tests for Nonfunctional Requirements}

% \wss{If there is a module that needs to be independently assessed for
%   performance, those test cases can go here.  In some projects, planning for
%   nonfunctional tests of units will not be that relevant.}

% \wss{These tests may involve collecting performance data from previously
%   mentioned functional tests.}

% \subsubsection{Module ?}
		
% \begin{enumerate}

% \item{test-id1\\}

% Type: \wss{Functional, Dynamic, Manual, Automatic, Static etc. Most will
%   be automatic}
					
% Initial State: 
					
% Input/Condition: 
					
% Output/Result: 
					
% How test will be performed: 
					
% \item{test-id2\\}

% Type: Functional, Dynamic, Manual, Static etc.
					
% Initial State: 
					
% Input: 
					
% Output: 
					
% How test will be performed: 

% \end{enumerate}

% \subsubsection{Module ?}



\subsection{Traceability Between Test Cases and Modules}

% \wss{Provide evidence that all modules have been considered.}
				
\bibliographystyle{plainnat}

\bibliography{../../refs/References}

\newpage

% \section{Appendix}

% This is where you can place additional information.

% \subsection{Symbolic Parameters}

% The definition of the test cases will call for SYMBOLIC\_CONSTANTS.
% Their values are defined in this section for easy maintenance.

% \subsection{Usability Survey Questions?}

% \wss{This is a section that would be appropriate for some projects.}

% \newpage{}
% \section*{Appendix --- Reflection}

% \wss{This section is not required for CAS 741}

% The information in this section will be used to evaluate the team members on the
% graduate attribute of Lifelong Learning.

% \input{../Reflection.text}

% \begin{enumerate}
%   \item What went well while writing this deliverable? 
%   \item What pain points did you experience during this deliverable, and how
%     did you resolve them?
%   \item What knowledge and skills will the team collectively need to acquire to
%   successfully complete the verification and validation of your project?
%   Examples of possible knowledge and skills include dynamic testing knowledge,
%   static testing knowledge, specific tool usage, Valgrind etc.  You should look to
%   identify at least one item for each team member.
%   \item For each of the knowledge areas and skills identified in the previous
%   question, what are at least two approaches to acquiring the knowledge or
%   mastering the skill?  Of the identified approaches, which will each team
%   member pursue, and why did they make this choice?
% \end{enumerate}

\end{document}